The letter

### 2010-06-29 ltx/PLoS/SubmissionLetter.tex

We hope that this work will inspire both theoreticians and experimentalists by providing a framework for linking continuum neural field models to patient-specific data. Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques. In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. This work provides an essential link, bridging the data driven and theoretically driven areas of research. We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.

@@

@@

Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.
\bibliographystyle{plain}
\bibliography{}
\end{document}

>>>>

This paper brings several new techniques to Computational Biology. We have developed a data-driven framework for generating patient-specific neural field models. This paper is timely and draws together several cutting-edge technologies:
\begin{itemize}
	\item Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques. 
	\item In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. 
	\item In addition, recent advances in computing power and nonlinear systems theory have made possible state estimation from nonlinear spatio-temporal systems.
\end{itemize}

We hope that this work will inspire both theoreticians and experimentalists by providing a framework for linking continuum neural field models to patient-specific data. This work provides an essential link, bridging the data driven and theoretically driven areas of research. We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.

@@

Since this primarily a methods paper, we have taken the option of preceding the results by the methods section.

@@

The authors.

(Dean Freestone, Parham Aram, Mike Dewar, Ken Scerri, David Grayden and Visakan Kadirkamanathan.)
\bibliographystyle{plain}
\bibliography{}
\end{document}
